Establishing Trusted I/O Paths for Client \\ Shielded Executions with Aurora

### 2019-08-24 article.tex
full paper review

\title{Establishing Trusted I/O Paths for \\ Client Shielded Executions with Aurora}

@@

Nowadays, users' sensitive data in edge computing devices (desktops, laptops, and tablets, etc.) is at high risk because they run applications on potentially compromised or malicious systems. To address this problem, hardware vendors propose Trusted Execution Environment (TEE). Particularly, Intel has released a new processor feature called Software Guard eXtension (SGX), and provisions shielded executions (i.e., enclaves) for security-sensitive computations. Regrettably, Intel SGX's design objectives omit trusted I/O paths. Without such guarantees, it is unlikely for an enclave to fulfill its security and privacy purposes because the source or sink of data may have been corrupted.

@@

In this paper, we present \textsc{Aurora}, a novel architecture that safeguards I/O paths of SGX enclaves. To directly communicate with hardware devices without depending on the untrusted software, \textsc{Aurora} introduces System Management RAM (SMRAM) as a special enclave. SMRAM is a tamper-proof memory region used only in System Management Mode (SMM), much like the enclave region with SGX protection in user mode. \textsc{Aurora} delegates I/O requests from enclaves to the SMI handler protected inside SMRAM. We call this particular SMI handler \textit{SMVisor}. In hardware, SMVisor is safe from any corruptions by other privileged software (including OS and hypervisor). Therefore, Intel SGX enclaves can safely use I/O devices while remaining \textit{transparent} to the underlying OS.

@@

\subsection{Threat Model}
We consider an adversary who can compromise the system via software attacks. He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify MMIO region, or change the operating mode of a device) and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. %The white areas denote the TCB.
	1) An output request is triggered by an enclave as an exception:
\textcircled{\scriptsize{1}} The user logic in an enclave issues an output request by invoking  Tlibaurora's APIs;
\textcircled{\scriptsize{2}} Tlibaurora marshals and encrypts the request's arguments, and invokes Ulibaurora outside the enclave to relay the request;
\textcircled{\scriptsize{3}} Ulibaurora \emph{ioctls} the ashmd module to trigger an \textit{smcall};
\textcircled{\scriptsize{4}} SMVisor is notified and obtains the encrypted requests from the secure session;
\textcircled{\scriptsize{5}} SMVisor decrypts the request and invokes the driver;
\textcircled{\scriptsize{6}} The driver processes output data in PCI space or MMIO buffer;
\textcircled{\scriptsize{7}} The driver returns a result code to SMVisor. In the end, SMVisor executes \textit{RSM} to return to protected mode. 
	2) An input request from an enclave causes a device interrupt:
\textcircled{\scriptsize{1}} The target device triggers an interrupt, and the control flow is rerouted to SMVisor which has the interrupt handler;
\textcircled{\scriptsize{2}} SMVisor invokes the driver to handle the input request;
\textcircled{\scriptsize{3}} The driver gets the raw input data and sends it to SMVisor;
\textcircled{\scriptsize{4}} SMVisor encrypts the data inside SMRAM, and sends it to the target enclave via the secure session;
\textcircled{\scriptsize{5}} The system switches back to protected mode and the ashmd module uses a signal to notify Ulibaurora;
\textcircled{\scriptsize{6}} Ulibaurora invokes Tlibaurora to receive the encrypted data;
\textcircled{\scriptsize{7}} The enclave decrypts the encrypted data and finally obtains the raw input data.
	}
	\label{fig:workflow}
\end{figure}

@@

\subsection{Trusted Hardware Clock}\label{time service}
The integrity and non-forgeability of the clock value is much more vital. In this section, we describe how to extend \textsc{Aurora} for trusted, high-resolution, absolute and attack-aware clock.

\textbf{Multiple Sources.}
%% 多源头获取时间，适应不同需求
\textsc{Aurora} uses multiple clock sources available on x86 platforms, such as programmable interval timer (PIT) and advanced configuration and power interface/power management (ACPI/PM) timer. To estimate the latency of obtaining time from hardware and adjust their values, SMVisor references invariant time stamp counter (TSC) via \textit{RDTSCP} instruction. The invariant TSC ensures that the duration of each clock tick is uniform (at the frequency relative to the crystal clock frequency of the processor core).

@@

\textbf{High Resolution.}
%% 根据时钟频率和差值计算时间精度
When a time value with high resolution (e.g. micro-second) is required, \textsc{Aurora} uses the invariant TSC and High Precision Event Timer (HPET) to satisfy the need. For instance, \textsc{Aurora} uses the following formulae to compute the \textit{tv\_usec} value in \textit{timeval} data structure: {$tv\_usec = (HPET\_value/ HPET\_Hz) / 1,000,000$;} where $(HPET\_value / HPET\_Hz)$ computes the absolute time in micro-seconds.

\textbf{Attack-Awareness.}
%% 如何避免时钟攻击
Though the hardware clocks can be controlled and modified by the malicious OS, diverse timers in Aurora offer enclaves the ability to validate the credibility of time values. Tlibaurora records last values read from all hardware clocks and obtains current values to calculate their differences respectively, and then uses clock frequencies to compute the actual elapsed time. When any of the measured time violates the monotonic rule, we assume a time attack.

@@

To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we wrote variable sizes of contents to a USB storage device on native Linux system as the baseline, by using \texttt{dd} program with options \texttt{fsync} and \texttt{direct}. To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device. % to bypass any file system interference. We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path. We did not use any encryption in this experiment.

The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB. \textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to the device. The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.

>>>>

\title{Establishing Trusted I/O Paths for Client \\ Shielded Executions with Aurora}

@@

Today users' private data in edge computing devices (desktops, laptops, and tablets, etc.) is at high risk because they run applications on potentially compromised or malicious systems. To address this problem, hardware vendors propose Trusted Execution Environment (TEE). Particularly, Intel has released a new processor feature called Software Guard eXtension (SGX), and provisions shielded executions (i.e., enclaves) for security-sensitive computations. Regrettably, Intel SGX's design objectives omit trusted I/O paths. Without such guarantees, it is unlikely for an enclave to fulfill its security and privacy purposes because the source or sink of data may have been corrupted.

@@

In this paper, we present \textsc{Aurora}, a novel architecture that safeguards I/O paths of SGX enclaves. To directly communicate with hardware devices without depending on the untrusted software, \textsc{Aurora} introduces System Management RAM (SMRAM) as a special enclave. SMRAM is a tamper-proof memory region used only in System Management Mode (SMM), much like the enclave region with SGX protection in user mode. \textsc{Aurora} delegates I/O requests from enclaves to the SMI handler protected inside SMRAM. We call this particular SMI handler \textit{SMVisor}. In hardware, SMVisor is safe from any corruptions by other privileged software. Therefore, Intel SGX enclaves can safely use I/O devices while remaining \textit{transparent} to the underlying OS and hypervisor.

@@

\subsection{Threat Model and Assumptions}
We consider an adversary who can compromise the system via software attacks. He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify MMIO region, or change the operating mode of a device) and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.49\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. %The white areas denote the TCB.
	1) An output request is triggered by an enclave as an exception:
\textcircled{\scriptsize{1}} The user logic in an enclave issues an output request by invoking  Tlibaurora's APIs;
\textcircled{\scriptsize{2}} Tlibaurora marshals and encrypts the request's arguments, and invokes Ulibaurora outside the enclave to relay the request;
\textcircled{\scriptsize{3}} Ulibaurora \emph{ioctls} the ashmd module to trigger an \textit{smcall};
\textcircled{\scriptsize{4}} SMVisor is notified and obtains the encrypted requests from the secure session;
\textcircled{\scriptsize{5}} SMVisor decrypts the request and invokes the driver;
\textcircled{\scriptsize{6}} The driver processes output data in PCI space or MMIO buffer;
\textcircled{\scriptsize{7}} The driver returns a result code to SMVisor. In the end, SMVisor executes \textit{RSM} to return to protected mode. 
	2) An input request from an enclave causes a device interrupt:
\textcircled{\scriptsize{1}} The target device triggers an interrupt, and the control flow is rerouted to SMVisor which has the interrupt handler;
\textcircled{\scriptsize{2}} SMVisor invokes the driver to handle the input request;
\textcircled{\scriptsize{3}} The driver gets the raw input data and sends it to SMVisor;
\textcircled{\scriptsize{4}} SMVisor encrypts the data inside SMRAM, and sends it to the target enclave via the secure session;
\textcircled{\scriptsize{5}} The system switches back to protected mode and the ashmd module uses a signal to notify Ulibaurora;
\textcircled{\scriptsize{6}} Ulibaurora invokes Tlibaurora to receive the encrypted data;
\textcircled{\scriptsize{7}} The enclave decrypts the encrypted data and finally obtains the raw input data.
	}
	\label{fig:workflow}
\end{figure}

@@

\subsection{Trusted Hardware Clock}\label{time service}
The integrity and non-forgeability of the clock value is much more vital. In this section, we describe how to extend \textsc{Aurora} for trusted, absolute, high-resolution and attack-aware clock.

%\textbf{Diverse Sources.}
%%% 多源头获取时间，适应不同需求
%\textsc{Aurora} uses multiple clock sources available on x86 platforms, such as programmable interval timer (PIT) and advanced configuration and power interface/power management (ACPI/PM) timer.

@@

\textbf{High Resolution.}
%% 根据时钟频率和差值计算时间精度
When a time value with high resolution (e.g. micro-second) is required, \textsc{Aurora} uses invariant time stamp counter (TSC) and High Precision Event Timer (HPET). For instance, \textsc{Aurora} uses the following formulae to compute the \textit{tv\_usec} value in \textit{timeval} data structure: {$tv\_usec = (HPET\_value/ HPET\_Hz) / 1,000,000$;} where $(HPET\_value / HPET\_Hz)$ computes the absolute time in micro-seconds. SMVisor references invariant TSC to estimate the latency of hardware response and adjust the value. Invariant TSC ensures that the duration of each clock tick is uniform.

\textbf{Attack-Awareness.}
%% 如何避免时钟攻击
Though hardware clocks can be controlled and modified by the malicious OS, diverse timers in Aurora offer enclaves the ability to validate the credibility of time values. Tlibaurora records last values read from all hardware clocks and obtains current values to calculate their differences respectively, and then uses clock frequencies to compute the actual elapsed time. When any of the measured time violates the monotonic rule, we assume a time attack.

@@

To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we wrote variable sizes of contents to a USB storage device on native Linux system as the baseline, by using \texttt{dd} program with options \texttt{fsync} and \texttt{direct}. To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device. % to bypass any file system interference. We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path. We did not use any encryption in this experiment. 
The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB. \textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to the device. The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.
